Recruiting Chapter

### 2021-05-19 text/tables_figures_may_2021.Rmd
draft changes results

  plot_characteristic(
    df = readRDS(file.path('.','..', 'assets', 'tables', str_c('table_ego_', 'pubu', '.RDS'))),
    '% Black/Latinx/Native', c('c1_lt10', 'c2_10to20', 'c3_20to50', 'c4_50+'), c('<10%', '10-20%', '20-50%', '50%+'), visit_count = TRUE
  )
```

@@

```{r ego-network-figure-region, fig.align = 'center', echo = FALSE, fig.cap = "Geographic region of visited private high schools"}
#knitr::include_graphics('./../assets/figures/ego_network_figure_region_pubu_privu_privc.pdf')
knitr::include_graphics('./../assets/figures/ego_network_figure_region_pubu_privu.pdf')
```

@@

```{r ego-network-figure-religion, fig.align = 'center', echo = FALSE, fig.cap = "Religious affiliation of visited private high schools"}
#knitr::include_graphics('./../assets/figures/ego_network_figure_religion_pubu_privu_privc.pdf')
knitr::include_graphics('./../assets/figures/ego_network_figure_religion_pubu_privu.pdf')
```

@@

```{r ego-network-figure-hs-rank, fig.align = 'center', echo = FALSE, fig.cap = "High school rank of visited private high schools"}
#knitr::include_graphics('./../assets/figures/ego_network_figure_hs_rank_pubu_privu_privc.pdf')
knitr::include_graphics('./../assets/figures/ego_network_figure_hs_rank_pubu_privu.pdf')
```

@@

```{r ego-network-figure-race, fig.align = 'center', echo = FALSE, fig.cap = "Racial composition of visited private high schools"}
#knitr::include_graphics('./../assets/figures/ego_network_figure_pct_black_latinx_native_pubu_privu_privc.pdf')
knitr::include_graphics('./../assets/figures/ego_network_figure_pct_black_latinx_native_pubu_privu.pdf')
```

@@

@@

```{r plot-1mode-privc, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "One-mode network for private liberal arts colleges, colored by cluster"}
knitr::include_graphics('./../assets/figures/plot_1mode_privc.pdf')
```

```{r plot-1mode-u, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "One-mode network for public and private universities, colored by cluster"}
knitr::include_graphics('./../assets/figures/plot_1mode_u.pdf')
```

@@

```{r plot-1mode-all, fig.align = 'center', echo = FALSE, eval=FALSE, out.width = "100%", fig.cap = "One-mode network for public universities, private universities, private liberal arts, colored by cluster"}
knitr::include_graphics('./../assets/figures/plot_1mode_all.pdf')
```

```{r plot-1mode-all-k5, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "One-mode network for public universities, private universities, private liberal arts, colored by cluster, five clusters"}
knitr::include_graphics('./../assets/figures/plot_1mode_all_k5.pdf')
```

@@

```{r two-mode-plot, fig.align = 'center', echo = FALSE, eval=FALSE, out.width = "100%", fig.cap = "2-mode network for all institutions, colored by geographic region"}
# <!-- plot of two-mode network; exclude for now -->
knitr::include_graphics('./../assets/figures/plot_2mode_all_region.pdf')

>>>>

  plot_characteristic(
    df = readRDS(file.path('.','..', 'assets', 'tables', str_c('table_ego_', 'pubu', '.RDS'))),
    '% Black/Latinx/Native', c('c1_lt10', 'c2_10to20', 'c3_20to50', 'c4_50+'), c('<10%', '10-20%', '20-50%', '50%+'), visit_count = TRUE
  )

# enrollment
  # pubu, privu, privc  
  run_plot_characteristics(which_psi = c('pubu','privu','privc'), which_char = 'g12_enroll', char_label = '12th grade enrollment', c('c1_lt50','c2_50to100','c3_100to150','c4_gt150'), c('LT 50','50-100','100-150','GT 150'))

  #run_plot_characteristics(which_psi = c('pubu','privu','privc'), which_char = 'g12_enroll', char_label = '12th grade enrollment', c('c1_lt100','c2_100to150','c3_150to200','c4_gt200'), c('LT 100','100-150','150-200','GT 200'))

  # pubu, privu
  run_plot_characteristics(which_psi = c('pubu','privu'), which_char = 'g12_enroll', char_label = '12th grade enrollment', c('c1_lt50','c2_50to100','c3_100to150','c4_gt150'), c('LT 50','50-100','100-150','GT 150'))

```

@@

```{r ego-network-figure-region, fig.align = 'center', echo = FALSE, fig.cap = "Geographic region of visited private high schools"}
knitr::include_graphics('./../assets/figures/ego_network_figure_region_pubu_privu_privc.pdf')
#knitr::include_graphics('./../assets/figures/ego_network_figure_region_pubu_privu.pdf')
```

@@

```{r ego-network-figure-religion, fig.align = 'center', echo = FALSE, fig.cap = "Religious affiliation of visited private high schools"}
knitr::include_graphics('./../assets/figures/ego_network_figure_religion_pubu_privu_privc.pdf')
#knitr::include_graphics('./../assets/figures/ego_network_figure_religion_pubu_privu.pdf')
```

@@

```{r ego-network-figure-g12-enroll, fig.align = 'center', echo = FALSE, fig.cap = "12th grade enrollment of visited private high schools"}
knitr::include_graphics('./../assets/figures/ego_network_figure_g12_enroll_pubu_privu_privc.pdf')
#knitr::include_graphics('./../assets/figures/ego_network_figure_g12_enroll_pubu_privu.pdf')
```

@@

```{r ego-network-figure-hs-rank, fig.align = 'center', echo = FALSE, fig.cap = "High school rank of visited private high schools"}
knitr::include_graphics('./../assets/figures/ego_network_figure_hs_rank_pubu_privu_privc.pdf')
#knitr::include_graphics('./../assets/figures/ego_network_figure_hs_rank_pubu_privu.pdf')
```

```{r ego-network-figure-race, fig.align = 'center', echo = FALSE, fig.cap = "Racial composition of visited private high schools"}
knitr::include_graphics('./../assets/figures/ego_network_figure_pct_black_latinx_native_pubu_privu_privc.pdf')
#knitr::include_graphics('./../assets/figures/ego_network_figure_pct_black_latinx_native_pubu_privu.pdf')
```

@@

```{r, echo = FALSE, eval = FALSE}
g_1mode_pubu <- g_1mode_pubu_psi

vertex_attr(graph=g_1mode_pubu, name='name') <- vertex_attr(graph=g_1mode_pubu, name='school_name')

m_1mode_pubu <- as_adjacency_matrix(
  #graph = g_1mode_u_psi,
  graph = g_1mode_pubu,
  type = "both",
  attr="weight",
  names = TRUE,
  #edges = TRUE,
  #sparse = igraph_opt("sparsematrices")
  sparse = FALSE
)

m_1mode_pubu
```

```{r, echo = FALSE, eval = FALSE}
g_1mode_privu <- g_1mode_privu_psi

vertex_attr(graph=g_1mode_privu, name='name') <- vertex_attr(graph=g_1mode_privu, name='school_name')

m_1mode_privu <- as_adjacency_matrix(
  #graph = g_1mode_u_psi,
  graph = g_1mode_privu,
  type = "both",
  attr="weight",
  names = TRUE,
  #edges = TRUE,
  #sparse = igraph_opt("sparsematrices")
  sparse = FALSE
)

m_1mode_privu
```

@@

```{r plot-1mode-u, fig.align = 'center', echo = FALSE, eval = FALSE, out.width = "100%", fig.cap = "One-mode network for public and private universities, colored by cluster"}
knitr::include_graphics('./../assets/figures/plot_1mode_u.pdf')
```

@@

```{r plot-2mode-u-k5, fig.align = 'center', echo = FALSE, eval = FALSE, out.width = "100%", fig.cap = "Two-mode network for public and private universities, colored by cluster, five clusters"}

knitr::include_graphics('./../assets/figures/plot_2mode_u_k5.pdf')

```{r plot-1mode-privc, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "One-mode network for private liberal arts colleges, colored by cluster"}
# appendix
knitr::include_graphics('./../assets/figures/plot_1mode_privc.pdf')
```

```{r plot-1mode-all-k5, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "One-mode network for public universities, private universities, private liberal arts, colored by cluster, five clusters"}
# appendix
knitr::include_graphics('./../assets/figures/plot_1mode_all_k5.pdf')
```

@@
